Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-19 latex/article.tex
latex editing

\subsection{LoD Criteria and Temporal Updates}

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to only
subdivide cells within the field of view.

>>>>

\subsection{Level of Details Criteria and Temporal Updates}

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to refine cells
within the camera frustrum. When rendering a mesh, a key stage is the
rasterization one which digitizes triangles projected onto the
screen. As a consequence, having several triangles whose projections
lie inside the same pixel is something we should prevent. Hence,
distance criterion can be set in order to both control the geometrical
approximation and to ensure that cells project onto more than one
pixel. Figure \ref{fig_lod_octree} illustrates the level of details
(LoD for short criterion) we use.

\begin{figure}
  \begin{center}
    \includegraphics[width=0.4\linewidth]{viewlod2_small}  
  \end{center}
  \caption{Adaptive meshing in dimension 2 using the LoD distance and
    angular criterion.}
  \label{fig_lod_octree} 
\end{figure}
